we will use built in data frae in R< for sparkR dataframe purpose.
This DataFrame includes 32 observations on 11 variables.

[, 1] mpg Miles/(US) --> gallon
[, 2] cyl --> Number of cylinders
[, 3] disp --> Displacement (cu.in.)
[, 4] hp --> Gross horsepower
[, 5] drat --> Rear axle ratio
[, 6] wt --> Weight (lb/1000)
[, 7] qsec --> 1/4 mile time
[, 8] vs --> V/S
[, 9] am --> Transmission (0 = automatic, 1 = manual)
[,10] gear --> Number of forward gears
[,11] carb --> Number of carburetors 

```{r}
load(mtcars)
library(sparkR)
head(mtcars)

## Initialize SQLContext. To work with dataframes we need a SQLContext which is created using `sparkRSQL.init(sp)`. SQLContext uses #SparkContext named `sp` here.Create the sp context for the purpose.
sqlContext <- sparkRSQL.init(sp)

## With SQLContext and a loaded local DataFrame, we create a Spark DataFrame:
sdf <- createDataFrame(sqlContext, mtcars) 
printSchema(sdf)
```

##Displays the content of the DataFrame

```{r}
SparkR::head(sdf)
```

## Selecting columns

```{r}
SparkR::head(select(sdf, sdf$mpg ))
```
##Filtering Data

```{r}
SparkR::head(SparkR::filter(sdf, sdf$mpg < 18))
```

## Operating on Columns

```{r}
# converting lb to metric ton- eneral airthmetics

sdf$wtTon <- sdf$wt * 0.45
SparkR::head(sdf)
```

##Grouping, Aggregation
-SparkR data frames support a number of commonly used functions to aggregate data after grouping. For example we can compute the average weight of cars by their cylinders as shown below:

```{r}
SparkR::head(summarize(groupBy(sdf, sdf$cyl), wtavg = avg(sdf$wtTon)))
# We can also sort the output from the aggregation to get the most common cars
car_counts <-summarize(groupBy(sdf, sdf$cyl), count = n(sdf$wtTon))
SparkR::head(arrange(car_counts, desc(car_counts$count)))
```

##Running SQL Queries from Spark DataFrames
-A Spark DataFrame can also be registered as a temporary table in Spark SQL and registering a DataFrame as a table allows you to run SQL queries over its data. The sql function enables applications to run SQL queries programmatically and returns the result as a DataFrame.

```{r}
# Register this DataFrame as a table.
registerTempTable(sdf, "cars")
# SQL statements can be run by using the sql method
highgearcars <- sql(sqlContext, "SELECT gear FROM cars WHERE cyl >= 4 AND cyl <= 9")
SparkR::head(highgearcars)
```



